Codebook
========

Codebook was generated on `r as.character(Sys.time())` using `r R.version$version.string`
during the same process that generated the dataset. 
See `run_analysis.R` for details on dataset creation.


Variable list and descriptions for *tidy.data*
----------------------------------------------

-------------------------------------------------------------------------------------------------|
Variable name |   Type       |  Description                                                      |
--------------|----------------------------------------------------------------------------------|
subject       | Factor w/ 30 | ID the subject who performed the activity for each window sample  |
activity      | Factor w/ 6  | Activity name                                                     |
value         | num          | Numeric value of measurement                                      |
domain        | Factor w/ 2  | Time domain signal or frequency domain signal (FREQUENCY or TIME) |
device        | Factor w/ 2  | Measuring instrument (ACCELEROMETER or GYROSCOPE)                 |
instrument    | Factor w/ 2  | Acceleration signal (BODY or GRAVITY)                             |
calculation   | Factor w/ 2  | Type of calculation which was made (MEAN or SD)                   |
jerk          | logi         | Is a jerk signal                                                  |
magnitude     | logi         | Is a magnitude of the signals calculated using the Euclidean norm |
axis          | Factor w/ 4  | 3-axial signals in the X, Y and Z directions (X or Y or Z or NA)  |
-------------------------------------------------------------------------------------------------|

Dataset structure
-----------------

```{r}
str(tidy.data)
```


Few rows of the dataset from head and tail
------------------------------------------

```{r}
head(tidy.data)

tail(tidy.data)
```

Summary of variables
--------------------

```{r}
summary(tidy.data)
```

Save to file
------------

Save tidy.data objects to a tab-delimited text file called `tidydata.txt`.

```{r}
f <- file.path(output_folder, "tidydata.txt")
write.table(tidy.data, f, quote = FALSE, sep = "\t", row.names = FALSE)
```





Variable list and descriptions for *tidy.data.avg*
--------------------------------------------------

-------------------------------------------------------------------------------------------------|
Variable name |   Type       |  Description                                                      |
--------------|----------------------------------------------------------------------------------|
subject       | Factor w/ 30 | ID the subject who performed the activity for each window sample  |
activity      | Factor w/ 6  | Activity name                                                     |
value         | num          | Numeric value of measurement                                      |
domain        | Factor w/ 2  | Time domain signal or frequency domain signal (FREQUENCY or TIME) |
device        | Factor w/ 2  | Measuring instrument (ACCELEROMETER or GYROSCOPE)                 |
instrument    | Factor w/ 2  | Acceleration signal (BODY or GRAVITY)                             |
calculation   | Factor w/ 2  | Type of calculation which was made (MEAN or SD)                   |
jerk          | logi         | Is a jerk signal                                                  |
magnitude     | logi         | Is a magnitude of the signals calculated using the Euclidean norm |
axis          | Factor w/ 4  | 3-axial signals in the X, Y and Z directions (X or Y or Z or NA)  |
count         | int          | Count of data points used to compute average                      |
average       | num          | Average of each variable for each activity and each subject       |
-------------------------------------------------------------------------------------------------|


Dataset structure
-----------------

```{r}
str(tidy.data.avg)
```


Few rows of the dataset from head and tail
------------------------------------------

```{r}
head(tidy.data.avg)

tail(tidy.data.avg)
```

Summary of variables
--------------------

```{r}
summary(tidy.data.avg)
```

Save to file
------------

Save tidy.data.avg objects to a tab-delimited text file called `tidydataavg.txt`.

```{r}
f <- file.path(output_folder, "tidydataavg.txt")
write.table(tidy.data.avg, f, quote = FALSE, sep = "\t", row.names = FALSE)
```




